%%
%% Glossary 
%%  for info: https://en.wikibooks.org/wiki/LaTeX/Glossary
%% can mix acronyms with `true' glossary entries if desired

\newglossaryentry{ele}{
  name=electron,
  description={a garbage particle for garbage people}
}

\newglossaryentry{photon}{
  name=photon,
  description={The photon is a type of elementary particle. It is the quantum of the electromagnetic field including electromagnetic radiation such as light and radio waves, and the force carrier for the electromagnetic force. Photons are massless, so they always move at the speed of light in vacuum, 299792458 m/s.},
  plural=photons,
}

\newglossaryentry{atlas}{
  name=A Toroidal LHC ApparatuS (ATLAS),
  description={ATLAS is the largest, general-purpose particle detector experiment at the Large Hadron Collider, a particle accelerator at CERN in Switzerland.}
}

\newglossaryentry{susy}{
  name=SUSY,
  description={Supersymmetry. An extension of the \gls{sm} which presents a new symmetry between fermions an bosons}
}

\newglossaryentry{fermion}{
  name=fermion,
  description={half integer spin particle}
}

\newglossaryentry{boson}{
  name=boson,
  description={integer spin particle}
}

\newglossaryentry{luminosity}{
  name=luminosty,
  description={Essentially the number of protons we have smashed together}
}

\newglossaryentry{quarks}{name=quarks, description={A quark is a type of elementary particle and a fundamental constituent of matter. Quarks combine to form composite particles called hadrons, the most stable of which are protons and neutrons, the components of atomic nuclei. All commonly observable matter is composed of up quarks, down quarks and electrons.}}

\newglossaryentry{lepton}{name=lepton, description={A lepton is an elementary particle of half-integer spin (spin 1/2) that does not undergo strong interactions.}}

\newglossaryentry{baryon}{name=baryon, description={A baryon is a type of composite subatomic particle which contains an odd number of valence quarks (at least 3). Baryons belong to the hadron family of particles}}

\newglossaryentry{jets}{name=jets, description={A jet is a narrow cone of hadrons and other particles produced by the hadronization of a quark or gluon in a particle physics or heavy ion experiment.}}

\newglossaryentry{hierarchy problem}{name=hierarchy problem, description={large quantum corrections to Higgs mass give non observed Higgs mass}}

\newglossaryentry{graviton}{name=graviton, description={theoretical force carrying particle for gravity}}

\newglossaryentry{run1}{name=Run 1, description={The LHC data-taking campaign from 2010 to 2012, operating at 7 TeV (2010-2011) and 8 TeV (2012) and with 50 ns bunch crossings.}}

\newglossaryentry{run2}{name=Run 2, description={The LHC data-taking campaign from 2015 to 2018, operating at 13 TeV and with 25 ns bunch crossings.}}

% key, acronym, long form
\newacronym{cern}{CERN}{European Organization for Nuclear Research} 
\newacronym{lhc}{LHC}{Large Hadron Collider}
\newacronym{lep}{LEP}{Large Electron-Positron}
\newacronym{alice}{ALICE}{A Large Ion Collider Experiment}
%\newacronym{atlas}{ATLAS}{A Large Toroidal LHC ApparatuS}
\newacronym{cms}{CMS}{Compact Muon Solenoid}
\newacronym{lhcb}{LHCb}{Large Hadron Collider beauty }
\newacronym{sm}{SM}{Standard Model}

\newacronym{qft}{QFT}{Quantum Field Theory}

\newacronym{trt}{TRT}{Transition Radiation Tracker}
\newacronym{gt}{gt}{Gauge Theory}
\newacronym{gut}{GUT}{Grand Unified Theory}
\newacronym{qcd}{QCD}{quantum chromodynamics}
\newacronym{hadronization}{hadronization}{hadronization}
\newacronym{qed}{QED}{quantum electrodynamics}
\newacronym{ewk}{EWK}{electroweak}
\newacronym{bsm}{BSM}{beyond the standard model}
\newacronym{pdf}{PDF}{parton distribution function}
%\newacronym{rpv}{RPV}{\rp violating}
%\newacronym{rpc}{RPC}{\rp conserving}
\newacronym{sfos}{SFOS}{same flavor opposite sign}
\newacronym{vev}{vev}{vacuum expectation value}




